---
title: "Réalisation de l'upset plot pour les ARGs de GMGC soil"
output: html_notebook
---

Librairies nécessaires :
```{r}
require(knitr)
require(dplyr)
require(readr)
require(tidyr)
require(ggplot2)
require(reshape2)
require(UpSetR)
```
VERSION POUR WATER
Modification du tableau sous forme de matrice.
```{r}
all_data <- read.csv("C:\\Users\\remi.gschwind\\Desktop\\Resfinder FG\\ResFinder_FG_Analysis\\analysis0422\\output\\soil\\all_soil.csv", sep = ";")
df <- tibble(gmgc_id = all_data$GMGC_id , family = all_data$family , db = all_data$db)
df2 <- df %>% separate_rows(db, sep = "/") %>% mutate(i = 1) %>% spread(db,i,fill=0)
df2
write.csv(df2, "C:\\Users\\remi.gschwind\\Desktop\\Resfinder FG\\ResFinder_FG_Analysis\\analysis0422\\output\\dataframe_soil.csv", row.names = FALSE)
```


On récupère les données
```{r}
# Import des données
data <- df2

# Conversion des double en integer et casting du tibble en dataframe
data <- data %>% mutate_if(is.numeric, as.integer)
data <- as.data.frame(data) 
```

On réalise un plot pour voir quelles sont les familles d'ATB importantes. 
```{r}
data %>% ggplot(aes(x = family)) + geom_bar() + coord_flip()
```
On selectionne les 6 familles les plus représentés 
Ici : Multidrug_efflux, Glycopeptide/Cycloserine, Rifampicin, Béta-lactamase, MLS et aminoside.

On ajoute une colonne au dataframe avec les nouveaux noms (le même ou other)
```{r}
data <- data %>% mutate(nametoshow = case_when(family == "Multidrug_efflux" ~ "Multidrug Efflux",
                                                family == "Glycopeptide/Cycloserine" ~ "Glycopeptide/Cycloserine",
                                                family == "Sulfonamide/trimethoprim" ~ "Sulfonamide/Trimethoprim",
                                                family == "MLS" ~ "MLS",
                                                family == "aminoside" ~ "Aminoside",
                                                family == "blactamase" ~ "Beta-lactamases",
                                                family == "cycline" ~ "Cycline",
                                                family == "phenicol" ~ "Phenicol",
                                                family == "quinolone" ~ "Quinolone",
                                                TRUE ~ "Others"))
```

Attribution des couleurs
```{r}
families <- c("Others", "Phenicol", "Cycline", "Quinolone", "Beta-lactamases", "Aminoside", "MLS", "Sulfonamide/Trimethoprim", "Glycopeptide/Cycloserine", "Multidrug Efflux")
colors_f <- c("#D2D2D2", "#8dd3c7", "#ffffb3", "#b3de69","#EE6666", "#BBDAEA", "#FCB6B6", "#FDCD8C", "#C0E69F", "#2C94DA") 
```

Réalisation de l'upset plot
```{r}
p <- UpSetR::upset(data,
              order.by = "freq", sets.x.label = "ARGs detected", point.size = 3, text.scale = 2.8,
              queries = list(
                list(query = elements,
                     params = list("nametoshow", families[1:10]),
                     color = colors_f[1],
                     active = T,
                     query.name = families[1]), 
              list(query = elements,
                     params = list("nametoshow", families[2:10]),
                     color =  colors_f[2],
                     active = T,
                     query.name = families[2]), 
              list(query = elements,
                     params = list("nametoshow", families[3:10]),
                     color = colors_f[3],
                     active = T,
                     query.name = families[3]),
              list(query = elements,
                     params = list("nametoshow", families[4:10]),
                     color = colors_f[4],
                     active = T,
                     query.name = families[4]),
              list(query = elements,
                     params = list("nametoshow", families[5:10]),
                     color = colors_f[5],
                     active = T,
                     query.name = families[5]),
              list(query = elements,
                     params = list("nametoshow", families[6:10]),
                     color = colors_f[6],
                     active = T,
                     query.name = families[6]),
              list(query = elements,
                     params = list("nametoshow", families[7:10]),
                     color = colors_f[7],
                     active = T,
                     query.name = families[7]),
              list(query = elements,
                     params = list("nametoshow", families[8:10]),
                     color = colors_f[8],
                     active = T,
                     query.name = families[8]),
              list(query = elements,
                     params = list("nametoshow", families[9:10]),
                     color = colors_f[9],
                     active = T,
                     query.name = families[9]),
              list(query = elements,
                     params = list("nametoshow", families[10:10]),
                     color = colors_f[10],
                     active = T,
                     query.name = families[10])
              ), query.legend = "top")

p
```

```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
